### 2023-09-13 README.Rmd
Updated readme

> Sjölander M., Linderholm, J., Geladi P., Buckland, P. I. (2023). _`r Title`_. (Journal name) <https://doi.org/xxx/xxx>

@@

> Sjölander M., Linderholm, J., Geladi P., Buckland, P. I. (2023). _`r Title`_. (Journal name) `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

>>>>

> Sjölander M., Linderholm, J., Geladi P., Buckland, P. I. (2023). _`r Title`_. (Journal of Archaeological Science:Reports) <https://doi.org/xxx/xxx>

@@

> Sjölander M., Linderholm, J., Geladi P., Buckland, P. I. (2023). _`r Title`_. (Journal of Archaeological Science:Reports) `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code in script files to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.pdf`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder: supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.
